%% Acronyms and definitions
%%Use this call in preample:
%\usepackage[nolist,nohyperlinks]{acronym}
%%\inlude these definitions after \maketitle (at least for REVTEX)
%%
\begin{acronym}[ACRONYM]
\acro{ct}[CT]{Catchy Title}
\acro{cpd}[CPD]{change point detection}
\acro{bp}[BP]{break point}
\acro{sm}[SM]{single-molecule}
\acro{smbj}[SMBJ]{single molecular break junction}
\acro{stm}[STM]{scanning tunneling microscope}
\acro{mcbj}[MCBJ]{mechanically controlled break junction}
\acro{bj}[BJ]{break junction}
\acro{iv}[IV]{current versus bias}
\acro{rt}[RT]{room temperature}
\acro{sam}[SAM]{self-assembled monolayer}
\acro{JMH}[JMH]{Dr. Joseph M. Hamill}
\acro{GCS}[GCS]{Prof. Gemma C. Solomon}
\acro{JOOJ}[JOOJ]{Prof. Jan O. O. Jeppesen}
\acro{ucph}[UCPH]{University of Copenhagen}
\acro{SG}[SG]{Solomon Group}
\acro{AH}[AH]{Prof. Andr\'{a}s Halbritter}
\acro{BME}[BME]{Budapest University of Technology and Economics}
\acro{NRL}[NRL]{Nano}
\acro{MHG}[MHG]{Marc Hamilton Garner}
\acro{rnn}[RNN]{recurrent neural network}
\acro{pca}[PCA]{principal component analysis}
\acro{uhv}[UHV]{ultra-high vacuum}
\acro{gap}[$\mathcal{G}$]{gap}
\acro{obj}[$\mathcal{O}$]{objective}
\acro{wp}[$\mathcal{W \mkern -7mu P}$]{work package}
\acro{EMRS}[E-MRS]{European Materials Research Society}
\acro{sota}[SOTA]{state-of-the-art}
\acro{odt}[ODT]{\odt}
\acro{ODT}[ODT]{\ODT}
\acro{bpy}[BPY]{\bpy}
\acro{thf}[THF]{\thf}
\acro{OPE3}[OPE3]{OPE3}
\acro{ope}[OPE]{\ope}
\acro{OPE}[OPE]{\OPE}
\acro{gmm}[GMM]{Gaussian mixture model}
\acro{3D}[3D]{three dimensional}\acused{3D}
\acro{adf}[ADF]{augemented Dickey-Fuller}
\acro{kpss}[KPSS]{Kwiatkowski–Phillips–Schmidt–Shin}
\acro{dfgls}[DFGLS]{augmented Dickey-Fuller with generalized least squares}
\acro{df}[DF]{Dickey-Fuller}
\acro{pp}[PP]{Phillips–Perron}
\acro{rss}[RSS]{residual sum of squares}
\acro{plh}[PLH]{plateau length histogram}
\acro{rms}[RMS]{root mean square}
\acro{itn}[ITN]{initial training network}
\acro{esr}[ESR]{early-stage researcher}
\acro{sdu}[SDU]{University of Southern Denmark}
\acro{ubern}[UniBern]{University of Bern}
\acro{ubham}[U. Birmingham]{University of Birmingham}
\acro{ml}[ML]{machine learning}
\acro{1DGH}[1DGH]{1D conductance histogram}
\acro{2DH}[2DH]{2D intensity plot}
\acro{daq}[DAQ]{data acquisition}
\acro{uroch}[U. Rochester]{University of Rochester}
\acro{JR}[JR]{Prof. Jascha Repp}
\acro{IF}[IF]{Prof. Ignacio Franco}
\acro{msca}[MSCA]{Marie Sk{\l}odowska-Curie Actions}
\acro{if}[IF]{Independent Fellowship}
\acro{qi}[QI]{quantum interference}
\acro{uregens}[U. Regensberg]{University of Regensberg}
\acro{JB}[JB]{Dr. James Bevington}
\acro{LAW}[LAW]{Dr. Luke A. Wilkinson}
\acro{ucl}[UCL]{University College, London}
\acro{uyork}[U. York]{University of York}
\acro{udurham}[U. Durham]{University of Durham}
\acro{LOD}[LOD]{Dr. Luke O'Driscoll}
\acro{SP}[SP]{Prof. Stergios Piligkos}
\acro{MP}[MP]{Prof. Michael Pittelko}
\acro{MBN}[MBN]{Prof. Mogens Br{\o}ndsted Nielsen}
\acro{dft}[DFT]{density functional theory}
\acro{cots}[COTS]{commercial off-the-shelf}
\acro{risk}[$\mathcal{R}$]{risk}
\acro{ms}[$\mathcal{M}$]{milestone}
\end{acronym}

%% Other abbreviations
% latin
\newcommand{\etal}{\textit{et al}}
\newcommand{\eg}{e.g.}
\newcommand{\ie}{i.e.}